On selection of a coupling method to cope with change of priors in one-vs-one classification

### 2025-05-28 appendix.tex
Fix typo in indexes

	Suppose there was a change of priors $\pi$ such that $\boldsymbol{R}^\pi$ would be belong to the one-parameter family $\boldsymbol{r}_s$ with $s$ in $(0,1)$. Then we have
	$$
	\boldsymbol{v}(\boldsymbol{R})^\pi = \boldsymbol{v}(\boldsymbol{R}^\pi) = \boldsymbol{v}(\boldsymbol{R}_s).
	$$
	Inverting action of $\pi$ would then determine $\boldsymbol{v}(\boldsymbol{R})$.

	In order to construct such $\pi$ let us introduce a new parametrization of the matrix of binary  predictions
	\begin{align}
		\begin{split}
			q_{12} &= \frac{1}{r_{12}} -1 \\
			q_{23} &= \frac{1}{r_{23}} -1 \\
			q_{31} &= \frac{1}{r_{31}} -1 
		\end{split}
	\end{align}
	Under the change of priors $\pi:\Pi \rightarrow \Pi' = (P'_1, P'_2, P'_3)$ we have
	\begin{align}
		q'_{ij}	= q_{ij} \cdot \frac{P_i'}{P_i} \frac{P_j}{P'_j}.
	\end{align}
	One checks easily that $\Pi' \propto (1, \frac{q_{12}}{q_{23}}, \frac{q_{12}}{q_{23}})$ yields the desired change of priors.

>>>>

	Suppose there was a change of priors $\pi$ such that $\boldsymbol{R}^\pi$ would be belong to the one-parameter family $\boldsymbol{R}_s$ with $s$ in $(0,1)$. Then we have
	$$
	\boldsymbol{v}(\boldsymbol{R})^\pi = \boldsymbol{v}(\boldsymbol{R}^\pi) = \boldsymbol{v}(\boldsymbol{R}_s).
	$$
	Inverting action of $\pi$ would then determine $\boldsymbol{v}(\boldsymbol{R})$.

	In order to construct such $\pi$ let us introduce a new parametrization of the matrix of binary  predictions
	\begin{align}
		\begin{split}
			q_{12} &= \frac{1}{r_{12}} -1 \\
			q_{23} &= \frac{1}{r_{23}} -1 \\
			q_{31} &= \frac{1}{r_{31}} -1 
		\end{split}
	\end{align}
	Under the change of priors $\pi:\Pi \rightarrow \Pi' = (P'_1, P'_2, P'_3)$ we have
	\begin{align}
		q'_{ij}	= q_{ij} \cdot \frac{P_i'}{P_i} \frac{P_j}{P'_j}.
	\end{align}
	One checks easily that $\Pi' \propto (1, \frac{q_{12}}{q_{23}}, \frac{q_{12}}{q_{31}})$ yields the desired change of priors.
